Lobbying and Legislative Uncertainty

### 2016-05-09 presentation.tex
change indicator var in presentation from X(1) to S(1)

%\documentclass{beamer} 
\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

@@

\title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
%\author[Kristy Buzard]{Kristy Buzard \\ Syracuse University and The Wallis Institute \\ kbuzard@syr.edu}
\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
\date{April 16, 2016}
\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

@@

\pause
Three legislators
\pause
\begin{itemize}
	\item Identified by location in linear preference space: $i \in \left\{-0.5,0,.5\right\}$
	\item Each will vote for status quo $\bm{s}$ or new proposal $\bm{x}$
	\item Decision made by majority vote
\end{itemize}

@@

\begin{frame}{Vote Buyer B}
\pause
Assume vote buyers maximize expected value of winning net of bribes paid  
\begin{itemize}[<+->]
	\item Assume bribes must be non-negative
	\item Vote buyer won't spend more than his willingness to pay, $W_B$
	\item In three-seat legislature, max probability that $\geq 2$ legislators vote for $s$
\end{itemize}
\end{frame}

\begin{frame}{Vote Buyer B's Objective Function}
\pause
Let $X(i) = 1$ denote legislator $i$ votes for the status quo
\begin{multline*}
			    \max_{b_{-.5}, b_0, b_{.5}} 
					W_B \biggl[ \Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(.5\right)=0\right)  + \\
					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(.5\right)=1\right) + \\
					\Pr\left(X\left(-.5\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) + \\
					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
				\end{multline*}
\end{frame}

\begin{frame}{Vote Buyer A}
\pause
Vote Buyer A is just like Vote Buyer B \textit{except}
\begin{itemize}[<+->]
	\item She gets to move first
	\item She wants $x$ to win instead of $s$
\end{itemize}
\end{frame}

>>>>

\documentclass{beamer} 
%\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

@@

\title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
%\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  
%\newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
\author[Buzard, DiTraglia and Saiegh \hspace{2.7in} \url{kbuzard@syr.edu}]{Kristy Buzard \inst{1} \and Frank DiTraglia \inst{2} \and Sebastian Saiegh \inst{3}}
\institute{\inst{1} Syracuse University and The Wallis Institute \and \inst{2} University of Pennsylvania \and \inst{3} UC San Diego}
\date{April 16, 2016}
\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\begin{frame}{Literature}
\pause
\begin{itemize}[<+->]
	\item \textbf{Probabilistic Voting with Policy Motivation}: Roemer 1994, 1997, Duggan $\&$ Fey 2011
	\item \textbf{Lobbying with Uncertainty}: Coates $\&$ Ludema 2001, Le Breton $\&$ Salanie 2003, Le Breton $\&$ Zaphorozhets (2007)
	\item \textbf{Vote Buying in Legislatures}: Groseclose $\&$ Snyder 1996, Banks 2000, Dal Bo 2007
	%\item \textbf{Uncertainty}: 
\end{itemize}
\end{frame}

@@

\pause
Three legislators
\pause
\begin{itemize}[<+->]
	\item Identified by location in linear preference space: $i \in \left\{-0.5,0,.5\right\}$
	\item Each will vote for status quo $\bm{s}$ or new proposal $\bm{x}$
	\item Decision made by majority vote
\end{itemize}

@@

\begin{frame}{Vote Buyer B}
\pause
Assume vote buyers maximize expected value of winning net of bribes paid  
\pause
\begin{itemize}[<+->]
	\item Assume bribes must be non-negative
	\item Vote buyer won't spend more than his willingness to pay, $W_B$
	\item In three-seat legislature, max probability that $\geq 2$ legislators vote for $s \times W_B -$ bribes
\end{itemize}
\end{frame}

\begin{frame}{Vote Buyer B's Objective Function}
\pause
Let $S(i) = 1$ denote legislator $i$ votes for the status quo
\pause
\begin{multline*}
			    \max_{b_{-.5}, b_0, b_{.5}} 
					W_B \biggl[ \Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=1\right)\left(S\left(.5\right)=0\right)  + \\
					\Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=0\right)\Pr\left(S\left(.5\right)=1\right) + \\
					\Pr\left(S\left(-.5\right)=0\right)\Pr\left(S\left(0\right)=1\right)\Pr\left(S\left(.5\right)=1\right) + \\
					\Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=1\right)\Pr\left(S\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
				\end{multline*}
\end{frame}

\begin{frame}{Vote Buyer A}
\pause
Vote Buyer A is just like Vote Buyer B \textit{except}
\pause
\begin{itemize}[<+->]
	\item She gets to move first
	\item She wants $x$ to win instead of $s$
\end{itemize}
\end{frame}
